%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Devansh Rastogi} \\ \vspace{10pt}
    \small \href{mailto:dvcam.rastogi1980@gmail.com}{\underline{devansh.rastogi6877@gmail.com}} $|$ 
    \href{https://linkedin.com/in/rastogidevansh}{\underline{linkedin.com/in/rastogidevansh}} $|$
    \href{https://github.com/primeDevansh}{\underline{github.com/primeDevansh}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology Madras}{Chennai, Tamil Nadu}
      {Bachelor of Science in Data Science and Applications}{Jan. 2024 -- Dec. 2027}
    \resumeSubheading
      {Guru Gobind Singh Indraprastha University}{Dwarka, Delhi}
      {Bachelor of Technology in Computer Science, Minor in AI \& ML}{Sep. 2021 -- July 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

	\resumeSubheading
      {Data Science Intern}{Feb. 2024 -- Mar. 2024}
      {IBM SkillsBuild | CSRBOX}{Remote}
      \resumeItemListStart
        \resumeItem{Acquired sound technical knowledge of data cleaning and preparation, statistical analysis and data visualization}
        \resumeItem{Tested this knowledge on the analysis of a real-world project through a case-study}
        \resumeItem{Learned to interpret the results of the analysis and presented them effectively}
      \resumeItemListEnd
      
	\resumeSubheading
      {Blockchain Developer}{Aug. 2023 -- Oct. 2023}
      {IBC Media}{Remote}
      \resumeItemListStart
        \resumeItem{Acquired good working knowledge of the Rust programming language and the Substrate framework}
        \resumeItem{Developed a blockchain-based decentralized application (dApp) on Polkadot}
        \resumeItem{Keenly absorbed smart contract intricacies and consensus mechanisms}
      \resumeItemListEnd

    \resumeSubheading
      {Liaison Officer}{July 2023}
      {G20 Conference on Crime and Security in the age of NFTs, AI \& Metaverse}{Gurugram, Haryana}
      \resumeItemListStart
        \resumeItem{Facilitated collaboration among G20 nations' representatives}
        \resumeItem{Ensured seamless communication on emerging NFT, AI, and Metaverse challenges}
        \resumeItem{Fostered collective strategies for global crime and security}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
    \resumeProjectHeading
%          {\textbf{\href{https://github.com/primeDevansh/hotel-reservation}{\underline{Hotel Reservation System}}} $|$ \emph{Ballerina, Choreo, React.js}}{Feb. 2024}
			{\textbf{Hotel Reservation System} $|$ \emph{Ballerina, Choreo, React.js}}{Feb. 2024}
          \resumeItemListStart
            \resumeItem{Implemented an API service using Ballerina programming language to demo a simple hotel reservation use case}
            \resumeItem{Developed front-end using React.js and built this project as a part of a buildathon conducted at my college}
            \resumeItem{Acquired sound technical knowledge about Ballerina and Choreo concepts}
            \resumeItem{Deployed the fully working Ballerina application on Azure cloud using Choreo}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Classify Song Genres from Audio Data} $|$ \emph{Python, NumPy}}{Jan. 2024 -- Feb. 2024}
          \resumeItemListStart
            \resumeItem{Applied machine learning algorithms to classify songs into genres}
            \resumeItem{Prepared the data set to apply principal component analysis (PCA)}
            \resumeItem{Trained a decision tree to classify the genre}
            \resumeItem{Used cross-validation to evaluate the models}
          \resumeItemListEnd
    
	\resumeProjectHeading
          {\textbf{Memorize!} $|$ \emph{Swift, SwiftUI}}{Nov. 2023 -- Dec. 2023}
          \resumeItemListStart
            \resumeItem{A tile-based memory challenge made using Swift and SwiftUI in Xcode}
            \resumeItem{User-selectable themes for a personalized gaming adventure}
            \resumeItem{Scores determined using accuracy and completion-time parameters}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Java, Python, R, SQL, Latex, Rust, Swift} \\
     \textbf{Frameworks}{: Docker, Substrate, SwiftUI, WordPress} \\
     \textbf{Developer Tools}{: Git/GitHub, DockerHub, VS Code, XCode, IntelliJ, Eclipse, RStudio, TeXShop} \\
}}
\end{itemize}

%
%----------EXTRA-CURRICULAR ACTIVITIES------
\section{Extra-Curricular Activities}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Basketball}{ Actively involved in college sports events - playing and organising} \\
     \textbf{YouTube}{ Technical YouTube channel to describe various issues faced by a coder along with optimal solutions} \\
     \textbf{Blog}{ Occasionally blog about life fundamentals and short stories}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
